---
title: "Replication package"
author: "Anne Keller and Richard Torkar"
date: "First version: 2021-03-18. Current version: `r Sys.time()`."
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = TRUE)
```

```{r setup2, include=FALSE}
library("openxlsx")
library("brms")
library("here") # make sure Rmd and Rproj root is the same
library("bayesplot")
```

# Introduction

This project is a part of a master thesis in software engineering. 


# Data

```{r}
d <- read.xlsx(here("data/SurveyDaTAV2.xlsx"), colNames = TRUE)
d <- d[complete.cases(d), ]
d <- d[d$Gender!=3,]
d$Age_s <- scale(d$Age)
nrow(d)
```

## Descriptive analysis

# 1 = female/transfemale, 2 = male/transmale
```{r}
table(d$Gender)
```

```{r}
summary(d$Age)
```

```{r}
summary(d$NrOfSub)
```

```{r}
table(d$NrOfSub)
```

# 1 = TV, 2 = Computer, 3 = Smartphone, 4 = Tablet, 5 = Other
```{r}
table(d$Device)
```

# 1 = none, 2 = 1 device, 3 = 2-3 devices, 4 = More than 4 devices
# Remove option 5
```{r}
table(d$ActiveDev)
```

# 1 = 0 days a week, 2 = 1-2 days a week, 3 = 3-4 days a week, 4 = 5-6 days a week
# 5 = Every day of the week
```{r}
table(d$DaysAWeek)
```

# 1 = 0 hours per day, 2 = Less than 1 hour, 3 = 1-2 hours, 4 = 3-4 hours, 5 = 5-6 hours, 6 = More than 7 hours per day
```{r}
table(d$HoursADay)
```

# Analysis

```{r}
m_c <- brm(
  O_Q8_1_5L ~ Age_s + Gender,
  family = cumulative(),
  data = d
)

m_ac <- brm(
  O_Q8_1_5L ~ Age_s + Gender,
  family = acat(),
  data = d
)

m_sr <- brm(
  O_Q8_1_5L ~ Age_s + Gender,
  family = sratio(),
  data = d
)

loo(m_c, m_ac, m_sr)
```

The above model comparison shows that there is no significant difference between the three models. This leaves us the option to pick a family we are comfortable working with. Since the \textsf{Cumulative} family has solid mathematical foundation we pick that one for our Likert scale outcomes.

```{r}
d$NrOfSub <- d$NrOfSub + 1

#m0 <- brm(
#  O_Q8_1_5L ~ 1,
#  family = cumulative(),
#  data = d
#)

#m1 <- brm(
#  O_Q8_1_5L ~ 1 + Age_s,
#  family = cumulative(),
#  data = d
#)

#m2 <- brm(
#  O_Q8_1_5L ~ 1 + Age_s + Gender,
#  family = cumulative(),
#  data = d
#)

# Outcome - Concern
# For the concern, gender as well as hours per day seem to be significant, negative impact
# PP check, seem to estimate quite well and the variance does not seem to large
# Looking at mcmc_areas the above is confirmed, also ActiveDev seem to have a negative # effect and DaysAWeek, Device and Age seem to have a positive effect

p <- get_prior(Concern ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,1)"
p$prior[c(14,15,16,17)] <- "dirichlet(2)"

m3 <- brm(
  Concern ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  # sample_prior = "only",
  data = d
)

pp_check(m3, type="bars", nsamples = 100)

mcmc_areas(m3, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m3)

# Outcome - Trust_Family
# No predictor seem to be significant
# pp check of the model looks good, check using different priors but made no difference
# The only predictor having any effect on the outcome is the device which have negative effect

p <- get_prior(Trust_Family ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,1)"
p$prior[c(14,15,16,17)] <- "dirichlet(2)"

m4 <- brm(
  Trust_Family ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m4, type="bars", nsamples = 100)

mcmc_areas(m4, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m4)

# Outcome - Trust_Scientist
# The gender seem to be significant in a negative direction concerning whether you trust a scientist or not
# ActiveDev as well as age does also seem to have a negative effect on the trust of scientist in relation to environmental information, Device has a positive impact

p <- get_prior(Trust_Scientist ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,1)"
p$prior[c(15,16,17,18)] <- "dirichlet(2)"

m5 <- brm(
  Trust_Scientist ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m5, type="bars", nsamples = 100)

mcmc_areas(m5, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m5)

# Outcome - Trust_Government
# Gender as well as ActiveDev seem to be significant, negative
# HoursADay looks to have a slightly negative impact whereas NrOfSub does have a slightly positive effect, neither significant

p <- get_prior(Trust_Government ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,1)"
p$prior[c(15,16,17,18)] <- "dirichlet(2)"

m6 <- brm(
  Trust_Government ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m6, type="bars", nsamples = 100)

mcmc_areas(m6, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m6)

# Outcome - Trust_EnergySupp
# Age is a significant predictor, negative impact
# pp check looks good
# Gender and DaysAWeek have a negative impact and NrOfSub do have a positive impact

p <- get_prior(Trust_EnergySupp ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,1)"
p$prior[c(15,16,17,18)] <- "dirichlet(2)"

m7 <- brm(
  Trust_EnergySupp ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m7, type="bars", nsamples = 100)

mcmc_areas(m7, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m7)

# Outcome - Trust_Environmental
# Age and gender are significant, negative impact
# ActiveDev does seem to have a slight negative effect

p <- get_prior(Trust_Environmental ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,1)"
p$prior[c(15,16,17,18)] <- "dirichlet(2)"

m8 <- brm(
  Trust_Environmental ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m8, type="bars", nsamples = 100)

mcmc_areas(m8, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m8)

# Outcome - Trust_Application
# Gender is significant, negative
# The pp check seem to be better with "normal(0,0.5)"
# Age as well as DaysAWeek seem to have a negative effect

p <- get_prior(Trust_Application ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,0.5)"
p$prior[c(15,16,17,18)] <- "dirichlet(2)"

m9 <- brm(
  Trust_Application ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m9, type="bars", nsamples = 100)

mcmc_areas(m9, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m9)

# Outcome - Trust_Media
# Gender is significant, negative
# Both Age, NrOfSub as well as Device have a negative effect

p <- get_prior(Trust_Media ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,1)"
p$prior[c(15,16,17,18)] <- "dirichlet(2)"

m10 <- brm(
  Trust_Media ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m10, type="bars", nsamples = 100)

mcmc_areas(m10, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m10)

# Outcome - Trust_Internet
# No predictor is significant
# pp check looked better with adjusted priors
# Age, Gender, Device, ActiveDev, DaysAWeek has all negative impact on the outcome
# NrOfSub has slight negative effect

p <- get_prior(Trust_Internet ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,0.5)"
p$prior[c(15,16,17,18)] <- "dirichlet(2)"

m11 <- brm(
  Trust_Internet ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m11, type="bars", nsamples = 100)

mcmc_areas(m11, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m11)

# Outcome - GiveUp
# Age is a significant predictor, negative
# pp check better with updated priors
# NrOfSub, ActiveDev as well as DaysAWeek seem to have a negative effect on the outcome whereas Gender, Device as well as HoursADay seem to hae a positive effect on the outcome, neither of the predictors are significant
# All predictors has some effect

p <- get_prior(Trust_GiveUp ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,0.5)"
p$prior[c(16,17,18,19)] <- "dirichlet(2)"

m12 <- brm(
  Trust_GiveUp ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m12, type="bars", nsamples = 100)

mcmc_areas(m12, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m12)

# Outcome - Act_WalkCycle
# Neither of the predictors are significant
# Age, Gender, ActiveDev and HoursADay have a positive impact on the outcome, NrOfSubs have a negative impact on the outcome

p <- get_prior(Act_WalkCycle ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,1)"
p$prior[c(16,17,18,19)] <- "dirichlet(2)"

m13 <- brm(
  Act_WalkCycle ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m13, type="bars", nsamples = 100)

mcmc_areas(m13, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m13)

# Outcome - Act_PublicTransport
# Adjusted priors
# Age and gender are significant, positive impact
# Device and HoursADay have a negative impact on the outcome, ActiveDev have a postive impact, neither are significant

p <- get_prior(Act_PublicTransport ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,0.5)"
p$prior[c(16,17,18,19)] <- "dirichlet(2)"

m29 <- brm(
  Act_PublicTransport ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m29, type="bars", nsamples = 100)

mcmc_areas(m29, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m29)

# Outcome - Act_TurnOffLights
# Age, NrOfSub, ActiveDev and HoursADay have a negative impact on the outcome but are not significant

p <- get_prior(Act_TurnOffLights ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,1)"
p$prior[c(16,17,18,19)] <- "dirichlet(2)"

m14 <- brm(
  Act_TurnOffLights ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m14, type="bars", nsamples = 100)

mcmc_areas(m14, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m14)

# Outcome - Act_Recycle
# Age has negative effect and gender has postive effect, both are significant factors
# ActiveDev has a positive impact, but not significant
# NrOfSub has a slight negative impact

p <- get_prior(Act_Recycle ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,1)"
p$prior[c(16,17,18,19)] <- "dirichlet(2)"

m15 <- brm(
  Act_Recycle ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m15, type="bars", nsamples = 100)

mcmc_areas(m15, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m15)

# Outcome - Act_Veggie
# Gender has a positive impact on the outcome, significant
# Age, ActiveDev, DaysAWeek has all positive impact on the outcome, but are not significant
# Device has a negative impact on the outcome

p <- get_prior(Act_Veggie ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,1)"
p$prior[c(16,17,18,19)] <- "dirichlet(2)"

m16 <- brm(
  Act_Veggie ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m16, type="bars", nsamples = 100)

mcmc_areas(m16, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m16)

# Outcome - Act_Computer
# Age has a significant negative effect on the outcome and NrOfSub has a significant positve effect on the outcome
# Gender, Device and ActiveDev has a negative effect and HoursADay has a positive effect, neither of them significant

p <- get_prior(Act_Computer ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,1)"
p$prior[c(16,17,18,19)] <- "dirichlet(2)"

m17 <- brm(
  Act_Computer ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m17, type="bars", nsamples = 100)

mcmc_areas(m17, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m17)


# Outcome - Act_Showers
# Age is significant negatively, NrOfSubs is significant positively
# After running pp check the priors were adjusted
# DaysAWeek, Device has a positive effect on the outcome, HoursADay has negative impact on the outcome

p <- get_prior(Act_Showers ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,0.5)"
p$prior[c(16,17,18,19)] <- "dirichlet(2)"

m18 <- brm(
  Act_Showers ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m18, type="bars", nsamples = 100)

mcmc_areas(m18, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m18)

# Outcome - Act_SecondHand
# Gender is significant, positive impact
# NrOfSub and ActiveDev has a positive impact, DaysAWeek and Device has a slight negative impact

p <- get_prior(Act_SecondHand ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,1)"
p$prior[c(16,17,18,19)] <- "dirichlet(2)"

m19 <- brm(
  Act_SecondHand ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m19, type="bars", nsamples = 100)

mcmc_areas(m19, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m19)

# Outcome - MainResp
# Age, NrOfSub and DaysAWeek does all have a negative impact on the outcome and ActiveDev and HoursADay have a positive impact on the outcome

p <- get_prior(MainResp ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,1)"
p$prior[c(15,16,17,18)] <- "dirichlet(2)"

m20 <- brm(
  MainResp ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m20, type="bars", nsamples = 100)

mcmc_areas(m20, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m20)

# Outcome - Motivate_Notif
# Significant Gender, negative
# Age, ActiveDev and HoursADay does all have a negative impact on the outcome

p <- get_prior(Motivate_Notif ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,1)"
p$prior[c(17,18,19,20)] <- "dirichlet(2)"

m21 <- brm(
  Motivate_Notif ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m21, type="bars", nsamples = 100)

mcmc_areas(m21, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m21)

# Outcome - Motivate_Information
# Gender, HoursADay are both significant negatively
# Age, NrOfSubs, ActiveDev does all have negative impact on the outcome
# DaysAWeek does have slight positive impact on the outcome

p <- get_prior(Motivate_Information ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,1)"
p$prior[c(17,18,19,20)] <- "dirichlet(2)"

m22 <- brm(
  Motivate_Information ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m22, type="bars", nsamples = 100)

mcmc_areas(m22, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m22)

# Outcome - Motivate_SetGoals
# HoursADay has a negative impact on the outcome and are significant
# Gender has a negative impact on the outcome

p <- get_prior(Motivate_SetGoals ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,1)"
p$prior[c(17,18,19,20)] <- "dirichlet(2)"

m23 <- brm(
  Motivate_SetGoals ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m23, type="bars", nsamples = 100)

mcmc_areas(m23, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m23)

# Outcome - Motivate_Nothing
# DaysAWeek has a negative an significant impact, HoursADay has a positive and significant impact
# ActiveDev and Gender has a positive effect on the outcome, Device has a negative impact on the outcome

p <- get_prior(Motivate_Nothing ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,1)"
p$prior[c(17,18,19,20)] <- "dirichlet(2)"

m24 <- brm(
  Motivate_Nothing ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m24, type="bars", nsamples = 100)

mcmc_areas(m24, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m24)

# Outcome - Motivate_LoggingUse
# Gender and HoursADay is significant and affects the outcome negatively
# ActiveDev affects the outcome negatively, Age, NrOfSub and Device affects the outcome negatively

p <- get_prior(Motivate_LoggingUse ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,1)"
p$prior[c(17,18,19,20)] <- "dirichlet(2)"

m25 <- brm(
  Motivate_LoggingUse ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m25, type="bars", nsamples = 100)

mcmc_areas(m25, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m25)

# Outcome - Motivate_Blocking
# Age, Gender, ActiveDev, DaysAWeek, HoursADay all have negative impact on the model, but not significant
# Device has a positive impact on the model, not significant

p <- get_prior(Motivate_Blocking ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,1)"
p$prior[c(17,18,19,20)] <- "dirichlet(2)"

m26 <- brm(
  Motivate_Blocking ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m26, type="bars", nsamples = 100)

mcmc_areas(m26, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m26)

# Outcome - Motivate_Impact
# Age is significant and negative
# Gender, NrOfSub, ActiveDev does all impact the outcome negatively
# Device does impact the outcome positively

p <- get_prior(Motivate_Impact ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,1)"
p$prior[c(17,18,19,20)] <- "dirichlet(2)"

m27 <- brm(
  Motivate_Impact ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m27, type="bars", nsamples = 100)

mcmc_areas(m27, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m27)

# Outcome - Motivate_Suggestions
# Gender is significant and negative
# NrOfSub, ActiveDev has negative impact on the outcome, Device has positive impact on the outcome

p <- get_prior(Motivate_Suggestions ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  data = d)

p$prior[1] <- "normal(0,1)"
p$prior[c(17,18,19,20)] <- "dirichlet(2)"

m28 <- brm(
  Motivate_Suggestions ~ 1 + Age_s + Gender + mo(NrOfSub) + Device + mo(ActiveDev) + mo(DaysAWeek) + mo(HoursADay),
  family = cumulative(),
  prior = p,
  data = d
)

pp_check(m28, type="bars", nsamples = 100)

mcmc_areas(m28, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^b_D", "^bsp"))

conditional_effects(m28)

#Plots

pp_check(m3, type="bars", nsamples = 100)
pp_check(m4, type="bars", nsamples = 100)
pp_check(m5, type="bars", nsamples = 100)
pp_check(m6, type="bars", nsamples = 100)
pp_check(m12, type="bars", nsamples = 100)

mcmc_areas(m3, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^bsp"))
mcmc_areas(m4, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^bsp"))
mcmc_areas(m5, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^bsp"))
mcmc_areas(m12, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^bsp"))
mcmc_areas(m13, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^bsp"))
mcmc_areas(m18, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^bsp"))
mcmc_areas(m19, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^bsp"))
mcmc_areas(m20, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^bsp"))
mcmc_areas(m24, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^bsp"))
mcmc_areas(m25, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^bsp"))
mcmc_areas(m27, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^bsp"))
mcmc_areas(m28, prob = 0.5, prob_outer = 0.95, regex_pars = c("^b_A", "^b_G", "^bsp"))

mcmc_trace(m28)

conditional_effects(m3)
conditional_effects(m4)
conditional_effects(m5)
conditional_effects(m6)
conditional_effects(m9)
conditional_effects(m28)

# p <- get_prior(mvbind(Concern,Trust_Family) ~ 1 + Age_s + Gender + mo(NrOfSub) + (1 | c | ID),
#   family = cumulative(),
#   data = d)
# 
# p$prior[1] <- "normal(0,1)"
# p$prior[2] <- "lkj(2)"
# p$prior[c(17,30)] <- "dirichlet(2)"
# 
# 
# m3_mv <- brm(
#   mvbind(Concern,Trust_Family) ~ 1 + Age_s + Gender + mo(NrOfSub) + (1 | c | ID),
#   family = cumulative(),
#   prior = p,
#   # sample_prior = "only",
#   data = d
# )
# 
# pp_check(m3_mv, type="bars", nsamples = 100, resp = "TrustFamily")
# 
# loo_compare(loo(m3), loo(m3_mv))



##m4 <- brm(
  ##Main.resp. ~ 1 + Active dev. + Days.a.week + Hours.a.day,
  ##family = cumulative(),
  ##data = d
##)


```

# Results